The transition redshift as a probe of reionization

### 2019-08-14 paper/ms.tex
Add info about survey overlap w 21cm
Add more stuff to detectability

In this work we will consider the prospect of performing intensity mapping
measurements of the H$\alpha$ line using the proposed, space-based Cosmic Dawn
Intensity Mapper (CDIM) \citep{2019arXiv190303144C}. CDIM is an infrared
telescope with an $83\,\text{cm}$ dish capable of measuring $R=300$ spectra
from wavelengths $0.75\,\mu\text{m}$ to $7.5\,\mu\text{m}$. Therefore, CDIM
will be able to measure the H-$\alpha$ line ($656\,\text{nm}$) from $z=0.14$
to $10.4$ and the H-$\beta$ line ($486\,\text{nm}$) from $z=0.54$ to $14.4$,
so long as there is a detectable signal. We choose to study the H-$\alpha$ and
H-$\beta$ lines since the uncertainty regarding their total intensity at
$z\sim10$ should be less uncertain than for lines that require metal
enrichment such as [\CII], [\OIII], or [\NII], since the total metal
enrichment of the universe is quickly declining at these high $z$

@@

The variance of the cross-spectrum between the 21~cm field and a line $i$ is
given by \citep[e.g.][]{2007ApJ...660.1030F}
\beq \label{eq:var_xps}
\Var{P_{21,i}} = P_{21,i}^2 + 
                                  P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
\eeq
where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
noise contribution. $P_{i,\text{tot}}$ is defined similarly.

@@

\section{To cite}
Papers that need to be cited:

The Cross-Correlation of High-Redshift 21 cm and Galaxy Surveys
\url{https://arxiv.org/abs/astro-ph/0611274}

Probing Reionization with the 21 cm-Galaxy Cross Power Spectrum
\url{https://arxiv.org/abs/0806.1055}

The HI Bias during the Epoch of Reionization, discusses the positive/negative
correlation transition as a function of $k$
\url{https://arxiv.org/abs/1907.05098}

>>>>

In this work we will consider the prospect of performing intensity mapping
measurements of the H$\alpha$ line using the proposed, space-based Cosmic Dawn
Intensity Mapper (CDIM) \citep{2019arXiv190303144C}. CDIM is an infrared
telescope with an $83\,\text{cm}$ dish capable of measuring $R=300$ spectra
from wavelengths $0.75\,\mu\text{m}$ to $7.5\,\mu\text{m}$. Therefore, CDIM
will be able to measure the H-$\alpha$ line ($656\,\text{nm}$) from $z=0.14$
to $10.4$ and the H-$\beta$ line ($486\,\text{nm}$) from $z=0.54$ to $14.4$,
so long as there is a detectable signal. CDIM will execute a wide, medium, and
deep survey of $311$, $31.1$, and $15.6\,\text{deg}^2$, respectively. However,
only the medium survey's field will overlap with 21~cm experiments (HERA and a
deep field from SKA1-LOW). Therefore we will only consider the medium survey.

We choose to study the H-$\alpha$ and H-$\beta$ lines since the uncertainty
regarding their total intensity at $z\sim10$ should be less uncertain than for
lines that require metal enrichment such as [\CII], [\OIII], or [\NII], since
the total metal enrichment of the universe is quickly declining at these high
$z$

@@

The variance per mode of the cross-spectrum between the 21~cm field and a line
$i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}
\beq \label{eq:var_xps}
\Var{P_{21,i}} = P_{21,i}^2 + 
                                  P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
\eeq
where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
noise contribution. $P_{i,\text{tot}}$ is defined similarly.

In detail $N_{\Ha}$ will have a frequency-dependent structure, but for
$z\sim9$ to $10$, it is reasonable to assume a conservative, constant value of
$N_{\Ha}\sim4\times10^4\,\text{Jy}/\text{sr}$ for the medium survey. For
$N_{21}$, we assume that $N_{21} = P_{21,21}(k=0.1\,\text{Mpc}^{-1})$, a
reasonable approximation given that HERA-350 will image some large scale modes
\citep{2017PASP..129d5001D}, as discussed previously \citep{2018ApJ...867...26B}.

The number of modes is given by,
\beq \label{eq:nmodes}
N_m = \frac{4\pi k^2 \delta k}{V_{\text{fund}}}\text{,}
\eeq
where $\delta k$ is the width of the $k$-bin and $V_{\text{fund}}$ is the
volume of a fundamental mode. We assume a square survey area, and so this is
given by,
\beq \label{eq:fund}
V_{\text{fund}} = \frac{(2 \pi)^3}{L_{\perp}^2 L_{\parallel}}\text{,}
\eeq
where $L_{\perp}$ is the  and $L_{\parallel}$ is the comoving
length of the redshift extent of the bin. The optimal redshift binning is not
entirely clear, since the observational target is not the power spectrum. We
assume a redshift bin of $\Delta z = 0.03$, which is smaller than the expected
error we compute on \zst{}, and so is not an unreasonable choice.

We assume a $k$-bin of fairly large width, from $k=0.1$ to $0.3\,\Mpc^{-1}$.

@@
